---
title: "Forwards and Options"
subtitle: "DM Chapter 2"
output: beamer_presentation
theme: "Madrid"
---

## Options

An **option** is a contract that gives the owner of the option the *right* but not the *obligation* to buy or sell an asset if they wish. This can be thought of as a contract where the transaction takes place only if it is profitable for the owner of the contract. 

Ownership of an option costs money upfront, called a **premium**.

## Options

Option terminology:

- Premium - The price to buy an option (not the asset)
- Strike Price - The agreed upon price that the asset is bought or sold for.
- Exercise - If it is profitable for the owner of the option, they will make the transaction happen. This is called exercising the option.
- Expiration date - the date after which the the option may no longer be exercised.
- European option - This type of option can only be exercised at the expiration date
- American Option - This type of option can be exercised at any point prior to the expiration date
- Spot price - The price of the underlying asset at any given time

We will mainly deal with European options. If I don't specify, I mean European option.


## Options

A **call option** is the right to buy an asset at expiration if the price is right

A **put option** is the right to sell an asset if the price is right

## Options

Suppose the car company purchased an option to buy steel at $400/ton at expiration. 

- If the spot price of steel at expiration was more than $400/ton, the car company would exercise the option and pay for the steel
-  If the spot price of steel at expiration was less than $400/ton, the car company would *NOT* exercise the option and make a payoff of 0

The payoff of a call option is $\mbox{max}(0, \mbox{Spot Price} - \mbox{Strike Price})$

## Options

```{r,fig.width = 4.5, fig.height = 3.5, echo=FALSE}
payoff <- function(x) 0 + (x - 40000)*(x > 40000) 
curve(payoff,from=30000,to=50000,main='Payoff Function for a Call Option',xlab='Spot Price',ylab='Payoff',col='blue',cex.main=.75,cex.axis=.75,cex.lab=.75,lwd = 2)
abline(h = 0)
points(40000,0,pch=4,col='red',cex=2)
```

## Options

Suppose that same car company purchased a put option to sell a fleet of cars in 1 year for $800,000. 

- If the price of the fleet of cars at expiration is more than 800,000, the car company will *NOT* exercise the put option and have a payoff of 0.
- If the price of the fleet of cars at expiration is less than 800,000, the car company will exercise the put option sell the fleet of cars.

The payoff of a put option is $\mbox{max}(0, \mbox{Strike Price} - \mbox{Spot Price})$

## Options

```{r,fig.width = 4.5, fig.height = 3.5, echo=FALSE}
payoff <- function(x) 0 + (800000-x)*(x < 800000) 
curve(payoff,from=700000,to=900000,main='Payoff Function for a Put Option',xlab='Spot Price',ylab='Payoff',col='blue',cex.main=.75,cex.axis=.75,cex.lab=.75,lwd = 2)
abline(h = 0)
points(800000,0,pch=4,col='red',cex=2)
```

## Options

Options will cost a premium at time 0. While payoff doesn't consider the premium, the **profit** will consider the premium. For both call and put options $$\mbox{Profit} = \mbox{Payoff} - \mbox{Future Value of Premium}$$

The logic here is that the money spent on the premium is either borrowed and accrues interest or can't be invested and the loss must be accumulated forward. 

## Options 

For this class, the interest rate is almost always *continuous*. So if P is the premium and the expiration time is t and the continuous interest rate is r, then the future value of the premium is $$Pe^{rt}$$

The time, t, is often measured in years. Having a premium doesn't change whether or not you exercise.

## Options 

Plotting profit as a function of spot price at expiration for an option must account for the premium.

```{r,fig.width = 4.5, fig.height = 3.5, echo=FALSE}
payoff <- function(x) 0 + (x - 40000)*(x > 40000)  - 1000
curve(payoff,from=30000,to=50000,main='Profit Function for a Call Option',xlab='Spot Price',ylab='Profit',col='blue',cex.main=.75,cex.axis=.75,cex.lab=.75,lwd = 2)
abline(h = 0)
points(40000,0,pch=4,col='red',cex=2)
```

## Options

```{r,fig.width = 4.5, fig.height = 3.5, echo=FALSE}
payoff <- function(x) 0 + (800000-x)*(x < 800000) - 10000
curve(payoff,from=700000,to=900000,main='Profit Function for a Put Option',xlab='Spot Price',ylab='Profit',col='blue',cex.main=.75,cex.axis=.75,cex.lab=.75,lwd = 2)
abline(h = 0)
points(800000,0,pch=4,col='red',cex=2)
```

## Practice

A call option is purchased for $12 to buy a stock with a strike price of 1000, an expiration date of 6 months. The risk free continuous interest rate is r = 4%. Determine the payoff and profit at expiration for the following spot prices at expiration:

- 950
- 1000
- 1010
- 1050

## Practice

A put option is purchased for $3 to sell a stock with a strike price of 40, with an expiration date of 4 months. The risk free continuous interest rate is r = 3%. Determine the spot price at expiration that would make this position have 0 profit.

## Moneyness

An option can be classified by its moneyness:

- In-the-money means that if the option was exercised immediately, it would make money
- Out-of-the-money means that if the option was exercised immediately, it would lose money
- At-the-money means that the option would break even if exercised immediately

The current spot price (not spot price at expiration) is compared to the strike price to determine the moneyness


